Enforced Invariant Confluence

### 2016-11-26 doc/counters.tex
Made TODOs conditionally compile.
istrong => istrong*

\subsection{\iconfluence{} Alternatives}
\begin{itemize}
  \item \todo{\istrength $\centernot \implies$ \isafety?}
  \item \todo{\isafety $\implies$ \istrength?}
  \item \todo{\istrength $\centernot \implies$ \iconfluence?}
  \item \todo{\iconfluence $\implies$ \istrength?}
  \item \todo{\istrengthstar $\implies$ \istrength?}
  \item \todo{\istrength $\implies$ \istrengthstar?}
  \item \todo{Find something between \isafety{} and \iconfluence.}
  \item \todo{1-iconfluence with derived txns to start}
\end{itemize}

@@

  \item \textbf{\istrengthstar{} \cite{gotsman2016cause}.}
    \leqnomode
    \begin{flalign*}
      & \exists G_0 \subseteq (\var \to \ints) \times (\var \to \ints).& \\
      & G_0(I) \subseteq I \land{} & \tag*{S2.} \\
      & \forall c, D, D'.\>
          D \in I \land
          (D, D') \in G_0^* \implies
          (D', D' \circ \denote{c}(D)) \in G_0 & \tag*{S3.}
    \end{flalign*}
    \reqnomode
    where $I$ is viewed as a set of database states.

  \item \textbf{\istrength{} \cite{gotsman2016cause}.}
    \leqnomode
    \begin{flalign*}
      & \exists G_0 \subseteq (\var \to \ints) \times (\var \to \ints). & \\
      & G_0(I) \subseteq I \land{} & \tag*{T2.} \\
      & \forall c.\>
        \exists P_1, \ldots, P_n \subseteq (\var \to \ints).\>
        \exists Q_1, \ldots, Q_n \subseteq (\var \to \ints).\> & \tag*{T3.} \\
      & \quad I \subseteq \cup_{i=1}^n P_i \land {} & \tag*{T3b.} \\
      & \quad \forall i \in \set{1, \ldots, n}.\> & \\
      & \quad \quad P_i \subseteq Q_i \land {} & \tag*{T3c.} \\
      & \quad \quad G_0(Q_i) \subseteq Q_i \land {} & \tag*{T3d.} \\
      & \quad \quad Q_i \times \denote{c}(P_i)(Q_i) \subseteq G_0 & \tag*{T3e.}
    \end{flalign*}
    \reqnomode
    where $I$ is viewed as a set of database states.
\end{itemize}

@@

@@

    \draw[ultra thick, impl] (0-isafety) -> (istrengthstar);
    \draw[ultra thick, impl] (istrengthstar) -> (iconfluence);
    \draw[ultra thick, impl] (0-isafety) -> (istrength);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
    \draw[impl] (istrengthstar) -> (ipreservation);
    \draw[impl] (0-isafety) -> (1-isafety);
    \draw[impl] (1-isafety) -> (k-isafety);
  \end{tikzpicture}

@@

      \inode[label=above:$D$]{s3a}{2, 1}
      \nnode[]{s3b}{2, 0}
      \inode[label=above:$D'$]{s3c}{3, 1}
      \nnode[]{s3d}{3, 0}
      \draw[txn] (s3a) -- (s3b) node[midway, left] {$\denote{c}(D)$};
      \draw[dgtxn] (s3c) -- (s3d) node[midway, right] {$\denote{c}(D)$};
      \draw[gtxn] (s3a) -- (s3c) node[midway, above] {$G_0^*$};
    \end{tikzpicture}
    \caption{\istrengthstar}
    \label{fig:istrengthstar}
  \end{subfigure}

>>>>

\subsection{\iconfluence{} Alternatives}
\begin{todoitemize}
  \item \todo{\istrength $\centernot \implies$ \isafety?}
  \item \todo{\isafety $\implies$ \istrength?}
  \item \todo{\istrength $\centernot \implies$ \iconfluence?}
  \item \todo{\iconfluence $\implies$ \istrength?}
  \item \todo{\istrengthstar $\implies$ \istrength?}
  \item \todo{\istrength $\implies$ \istrengthstar?}
  \item \todo{Find something between \isafety{} and \iconfluence.}
  \item \todo{1-iconfluence with derived txns to start}
\end{todoitemize}

@@

  \item \textbf{\istrengthstar{} \cite{gotsman2016cause}.}
    \leqnomode
    \begin{flalign*}
      & \exists G_0 \subseteq \dbs \times \dbs.& \\
      & G_0(I) \subseteq I \land{} & \tag*{S2.} \\
      & \forall c, D, D'.\>
          D \in I \land
          (D, D') \in G_0^* \implies
          (D', D' \circ \denote{c}(D)) \in G_0 & \tag*{S3.}
    \end{flalign*}
    \reqnomode
    where $I$ is viewed as a set of database states.

  \item \textbf{\istrength{} \cite{gotsman2016cause}.}
    \leqnomode
    \begin{flalign*}
      & \exists G_0 \subseteq \dbs \times \dbs. & \\
      & G_0(I) \subseteq I \land{} & \tag*{T2.} \\
      & \forall c.\>
        \exists P_1, \ldots, P_n \subseteq \dbs.\>
        \exists Q_1, \ldots, Q_n \subseteq \dbs.\> & \tag*{T3.} \\
      & \quad I \subseteq \cup_{i=1}^n P_i \land {} & \tag*{T3b.} \\
      & \quad \forall i \in \set{1, \ldots, n}.\> & \\
      & \quad \quad P_i \subseteq Q_i \land {} & \tag*{T3c.} \\
      & \quad \quad G_0(Q_i) \subseteq Q_i \land {} & \tag*{T3d.} \\
      & \quad \quad Q_i \times \denote{c}(P_i)(Q_i) \subseteq G_0 & \tag*{T3e.}
    \end{flalign*}
    \reqnomode
    where $I$ is viewed as a set of database states.
\end{itemize}

@@

\begin{claim}\label{clm:istrength-implies-istrengthstar}
  \istrength{} $\implies$ \istrengthstar{}.
\end{claim}
\begin{proof}
  Consider an arbitrary set of \imp{} transactions $T$ that is \istrong{} with
  respect to invariant $I$ with relation $G_0$ and sets $P_1^c, \ldots, P_n^c,
  Q_1^c, \ldots, Q_n^c$ for every $c \in T$. We show $T$ is \istrongstar{} with
  respect to $I$ with $G_0$.

  T2 implies S2. To prove S3, consider an arbitrary transaction $c$ and
  database states $D$ and $D'$ where $I(D)$ and $(D, D') \in G_0^*$. By T3b, $D
  \in P_i^c$ for some $i$, and by T3c, $D \in Q_i^c$. By T3d, $D' \in Q_i^c$.
  Finally by T3e, $(D', D' \circ \denote{c}(D)) \in G_0$.
\end{proof}

@@

    \draw[ultra thick, impl] (0-isafety) -> (istrengthstar);
    \draw[ultra thick, impl] (istrengthstar) -> (iconfluence);
    \draw[ultra thick, impl] (0-isafety) -> (istrength);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
    \draw[impl] (istrengthstar) -> (ipreservation);
    \draw[impl] (0-isafety) -> (1-isafety);
    \draw[impl] (1-isafety) -> (k-isafety);
    \draw[impl] (istrength) -> (istrengthstar);
  \end{tikzpicture}

@@

      \inode[label=above:$D$]{s3a}{2, 1}
      \nnode[]{s3b}{2, 0}
      \nnode[label=above:$D'$]{s3c}{3, 1}
      \nnode[]{s3d}{3, 0}
      \draw[txn] (s3a) -- (s3b) node[midway, left] {$\denote{c}(D)$};
      \draw[dgtxn] (s3c) -- (s3d) node[midway, right] {$\denote{c}(D)$};
      \draw[gtxn] (s3a) -- (s3c) node[midway, above] {$G_0^*$};
    \end{tikzpicture}
    \caption{\istrengthstar}
    \label{fig:istrengthstar}
  \end{subfigure}
